---
title: "Hotels"
author: "GS"
date: "4/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, comment = '')
```


Loading packages
```{r}
library(tidyverse)
library(tidymodels)
library(vip)
theme_set(theme_bw())
```

We will build a model to predict which actual hotel stays included children and/or babies, and which did not. 

Loading dataset
```{r}
hotels <- 
  read_csv('https://tidymodels.org/start/case-study/hotels.csv') %>% 
  mutate_if(is.character, as.factor)
```
## Checking data
```{r}
glimpse(hotels)
colSums(is.na(hotels))
```

Outcome variable 'children' is a factor variable with two levels
```{r}
 hotels %>% 
  count(children) %>% 
  mutate(prop = n/sum(n))
```

## Data splitting
```{r}
set.seed(2021)
hotels_split <- initial_split(hotels,
                              prop= .75,
                              strata = children)

hotel_train <- training(hotels_split)
hotel_test <- testing(hotels_split)
```
## Data resampling (CV)
```{r}
hotel_cv <- vfold_cv(hotel_train, v = 10)
```

# Penalized model
```{r}
pen_model <- 
  logistic_reg(penalty = tune(), mixture = 1) %>% 
  set_engine('glmnet')
```

```{r}
holidays <- c("AllSouls", "AshWednesday", "ChristmasEve", "Easter", 
              "ChristmasDay", "GoodFriday", "NewYearsDay", "PalmSunday")

pen_rec <- 
  recipe(children ~ ., data = hotel_train) %>% 
  step_date(arrival_date) %>% 
  step_holiday(arrival_date, holidays = holidays) %>% 
  step_rm(arrival_date) %>% 
  step_dummy(all_nominal(), -all_outcomes()) %>% 
  step_zv(all_predictors()) %>% 
  step_normalize(all_predictors())
```

```{r}
pen_wf <- 
  workflow() %>% 
  add_model(pen_model) %>% 
  add_recipe(pen_rec)
```

## Grid generation
```{r}
pen_reg_grid <- tibble(penalty = 10^seq(-4, -1, length.out = 30))
```


## Run the model
```{r, cache=TRUE}
pen_res <- 
  tune_grid(
    pen_wf,
    resamples = hotel_cv,
    grid = pen_reg_grid,
    control = control_grid(save_pred = T),
    metrics = metric_set(roc_auc)
  )
pen_res
```
## Metrics
```{r}
pen_metrics <- 
  pen_res %>% 
  collect_metrics()
pen_metrics  

```
## Plots metrics
```{r}
pen_metrics %>% 
  ggplot(aes(x = penalty, y= mean)) +
  geom_point() +
  geom_line() + 
  scale_x_log10(labels = scales::label_number())
```
## Best penalized models
```{r}
top_models <- 
  pen_res %>% 
  show_best(metric = 'roc_auc') %>% 
  arrange(penalty)

top_models

pen_best <- pen_res %>% 
  select_best()
pen_best

```


## AUC
```{r}
pen_auc <- 
  pen_res %>% 
  collect_predictions(parameters = pen_best) %>% 
  roc_curve(children, .pred_children) %>% 
  mutate(model = "Logistic Regression")

autoplot(pen_auc)
  
```


# Random Forest

```{r}
cores <- parallel::detectCores()
cores
```

## RF Model
```{r}
rf_mod <- 
  rand_forest(mtry = tune(), min_n = tune(), trees = 500) %>% 
  set_engine("ranger", num.threads = cores) %>% 
  set_mode("classification")
```

## RF Recipe
```{r}
rf_rec <- 
  recipe(children ~ ., data = hotel_train) %>% 
  step_date(arrival_date) %>% 
  step_holiday(arrival_date) %>% 
  step_rm(arrival_date) 
```

## RF workflow
```{r}
rf_wf <- 
  workflow() %>% 
  add_model(rf_mod) %>% 
  add_recipe(rf_rec)
```

```{r}
rf_mod
rf_wf

rf_mod %>% parameters
```
## Run RF model
```{r, cache=TRUE}
set.seed(2021)
rf_res <- 
  tune_grid(rf_wf,
            resamples = hotel_cv,
            grid = 20,
            control = control_grid(save_pred = TRUE),
            metrics = metric_set(roc_auc))
```

## Metrics
```{r}
rf_res %>% show_best(metric = 'roc_auc')
rf_best <- rf_res %>% select_best(metric = 'roc_auc')
```

```{r}
autoplot(rf_res)
```

```{r}
rf_auc <- 
  rf_res %>% 
  collect_predictions(parameters = rf_best) %>% 
  roc_curve(children, .pred_children) %>% 
  mutate(model = "Random Forest")
```


```{r}
bind_rows(rf_auc, pen_auc) %>% 
  ggplot(aes(x = 1 - specificity, y = sensitivity, col = model)) + 
  geom_path(lwd = 1.5, alpha = 0.8) +
  geom_abline(lty = 3) + 
  coord_equal() + 
  scale_color_viridis_d(option = "plasma", end = .6)
```

```{r, cache=TRUE}
last_rf_mod <- 
  rand_forest(mtry = 8, min_n = 7, trees = 500) %>% 
  set_engine("ranger", num.threads = cores, importance = "impurity") %>% 
  set_mode("classification")

# the last workflow
last_rf_workflow <- 
  rf_wf %>% 
  update_model(last_rf_mod)

# the last fit
set.seed(2021)
last_rf_fit <- 
  last_rf_workflow %>% 
  last_fit(hotels_split)

last_rf_fit
```

```{r}
last_rf_fit %>% 
  collect_metrics()
```


```{r}
last_rf_fit %>% 
  pluck(".workflow", 1) %>%   
  pull_workflow_fit() %>% 
  vip(num_features = 20)
```


```{r}
last_rf_fit %>% 
  collect_predictions() %>% 
  roc_curve(children, .pred_children) %>% 
  autoplot()
```
























































